A studyforrest extension, an annotation of words and phonemes in the German dubbed movie ``Forrest Gump'' and its audio-description

### 2020-04-15 paper/main.tex
Add hint on endfloat
Remove the internal label 'research cut'

% For more detailed article preparation guidelines, please see:
% http://f1000research.com/author-guidelines
\documentclass[10pt,a4paper,onecolumn]{article}
\usepackage{f1000_styles}
\geometry{right=4cm}
\usepackage{booktabs}
\usepackage[
	colorlinks=true,
	urlcolor=blue,
	linkcolor=green
]{hyperref}
%% Default: numerical citations
\usepackage[numbers]{natbib}

@@

\section*{Materials and methods}
\subsection*{Stimulus}
% References sind vom Anno-Paper in die .bib-Datei übernommen worden; die
% “hardcoded” Zitationen sind aber noch im laufenden Text.
We annotated speech in the slightly shortened ``research cut'' of the movie
\citep{hanke2016simultaneous} and its temporally aligned audio-description
\citep{hanke2014audiomovie}. For the movie stimulus, we used the audio track of
the German DVD release (Paramount Home Entertainment, Germany, 2002; PAL video,
DE103519SV)\citep{ForrestGumpDVD}. For the audio-only stimulus, we used the
movie's audio-description that was broadcast as an additional audio track for
visually impaired listeners on Swiss public television (Koop, Michalski,
Beckmann, Meinhardt \& Benecke, produced by Bayrischer Rundfunk,
2009)\citep{ForrestGumpGermanAD}. The plot of the movie is already carried by an
off-screen voice of the main character Forrest Gump. In the largely identical audio-description, a male narrator additionally describes essential aspects of the visual scenery when there is no off-screen voice, dialog, or other relevant auditory content
\subsection*{Annotation procedure}
% wo kommen die "preliminaries transcriptions" her?
% Die "most basic" Datei, die das Dataset enthält ist der Merge aus Diaolog, Narrator & Non-Speech-Annotation
Preliminary, orthographic transcriptions of dialogues (german\_dialog.csv),
non-speech vocalizations (e.g. laughing or groaning;
non\_speech\_vocalization.json), and the audio-description's narrator
(german\_audio\_description.csv) were merged and converted to Praat's
\citep{boersma2019praat} .TextGrid format (
\href{www.fon.hum.uva.nl/praat}{fon.hum.uva.nl/praat}). The merged transcription
containing one onset and offset for usually a couple of sentences was opened
along (the audio file of) the audio-description in Praat v6.0.22 for manual
improvements: In several passes, the approximate temporal onsets and offsets
were corrected. Intervals containing several sentences were split into intervals
containing only one sentence. When two or more persons were speaking
simultaneously the less dominant (background) voice was dropped. Low volume
background speech (especially occurring during music or continuous environmental
noise) or low volume non-speech vocalizations that are difficult to recognize by
a regular audience were dropped, too.

>>>>

% For more detailed article preparation guidelines, please see:
% http://f1000research.com/author-guidelines
\documentclass[10pt,a4paper,onecolumn]{article}
\usepackage{f1000_styles}
\geometry{right=4cm}
% enable the 'endfloat' package to sort all tables and figures to the
% end of the document without having to edit the manuscript
%\usepackage{endfloat}
\usepackage{booktabs}
\usepackage[
	colorlinks=true,
	urlcolor=blue,
	linkcolor=green
]{hyperref}
%% Default: numerical citations
\usepackage[numbers]{natbib}

@@

\section*{Materials and methods}
\subsection*{Stimulus}
% References sind vom Anno-Paper in die .bib-Datei übernommen worden; die
% “hardcoded” Zitationen sind aber noch im laufenden Text.
We annotated speech in stimuli built from the motion picture ``Forrest Gump'' as
used in two previous studies: an audio-visual movie
\citep{hanke2016simultaneous}, and its temporally aligned audio-description
\citep{hanke2014audiomovie}. For the movie stimulus, we used the audio track of
the German DVD release (Paramount Home Entertainment, Germany, 2002; PAL video,
DE103519SV)\citep{ForrestGumpDVD}. For the audio-only stimulus, we used the
movie's audio-description that was broadcast as an additional audio track for
visually impaired listeners on Swiss public television (Koop, Michalski,
Beckmann, Meinhardt \& Benecke, produced by Bayrischer Rundfunk,
2009)\citep{ForrestGumpGermanAD}. The plot of the movie is already carried by an
off-screen voice of the main character Forrest Gump. In the largely identical audio-description, a male narrator additionally describes essential aspects of the visual scenery when there is no off-screen voice, dialog, or other relevant auditory content
\subsection*{Annotation procedure}
% wo kommen die "preliminaries transcriptions" her?
% Die "most basic" Datei, die das Dataset enthält ist der Merge aus Diaolog, Narrator & Non-Speech-Annotation
Preliminary, orthographic transcriptions of dialogues (german\_dialog.csv),
non-speech vocalizations (e.g. laughing or groaning;
non\_speech\_vocalization.json), and the audio-description's narrator
(german\_audio\_description.csv) were merged and converted to Praat's
\citep{boersma2019praat} .TextGrid format (
\href{www.fon.hum.uva.nl/praat}{fon.hum.uva.nl/praat}). The merged transcription
containing one onset and offset for usually a couple of sentences was opened
along (the audio file of) the audio-description in Praat v6.0.22 for manual
improvements: In several passes, the approximate temporal onsets and offsets
were corrected. Intervals containing several sentences were split into intervals
containing only one sentence. When two or more persons were speaking
simultaneously the less dominant (background) voice was dropped. Low volume
background speech (especially occurring during music or continuous environmental
noise) or low volume non-speech vocalizations that are difficult to recognize by
a regular audience were dropped, too.
